Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
WIP on intro

Henry is five and an half, and has been diagnosed with visuo-constructive
deficits. He is under the care of an occupational therapist, and tries to improve
his inability to draw letters in a consistent manner. Diego is six and struggles
at school with his poor handwriting and even poorer self-confidence.

While Henry is lively and always quick at shifting his attention from one
activity to another, Diego is shy and poised. Two very different children,
facing however the same difficulty to write in a legible manner.

@@

Remediations for handwriting difficulties

@@

>>>>

Henry is five and an half, and has been diagnosed with visuo-constructive
deficits. He is under the care of an occupational therapist, and tries to
workaround his inability to draw letters in a consistent manner. Diego is six
and struggles at school with his poor handwriting and even poorer
self-confidence.

While Henry is lively and always quick at shifting his attention from one
activity to another, Diego is shy and poised. Two very different children,
facing however the same difficulty to write in a legible manner. And, hidden
behind this impaired skill, psycho-social difficulties also arise: they
underperform at school, Henry has to go for follow-up visits to a therapist,
they require ``special care''. This is a source of anxiety, for the children,
and for their parents alike.

@@

Remediations for handwriting difficulties traditionally involve
long interventions (at least 10 weeks~\cite{Hoy2011}), essentially handwriting
training with an occu therapist, and primarly address the motor deficits.
Improvements in self-confidence, anxiety occur (at best) as a consequence of the
child improving his/her handwriting skills and improving his/her performances at
school (when not too late).

We present in this article a new take on this educative challenge, as a
remediation procedure that involve a bad-writer robot that is taught by the
child: by building on the \emph{learning by teaching} paradigm, not only the
child practises hand-writing but, as he/she takes on the role of the teacher,
he/she also positively reinforce his/her self-esteem and motivation (he/she
shifts from the ``underperformer'' to become ``the one who knows and teaches'').

@@

\paragraph{Engagement levels}

A conclusion drawn in a systematic review of classical handwriting
interventions~\cite{Hoy2011} is that any of the studies considered which
involved fewer than two practice sessions per week and fewer than a total of 20
practice sessions, including homework, were not found to demonstrate effective
results. This highlights the necessity to engage students in an interaction
which will be sustainable over the long-term if we want to address research
questions which involve the measurement of learning gains.
